\name: A Non-Parametric, Hierarchical Wavelength-Calibration Model for a Precision Spectrograph

### 2020-05-06 paper/paper.tex
Wavelength Calibration Review
It's not a good review, but hopefully good enough to not make anyone mad

\lz{review of how wavelength solution has been done in the past.  Make the point that traditional wavelength solutions only make use of each calibration information independently
i.e. the standard method for wavelength calibration is...citations}

>>>>

Traditionally, wavelength solutions are constructed by fitting a polynomial to lines from a calibration source to describe the relationship between wavelength and pixel for each echelle order \citep{lovis2007, cersullo2019}.  Each calibration image is treated independently, though the entire set of calibration images has been used to vet incongruous lines \citep{coffinet2019}.  Just recently, work has been done that suggests a segmented polynomial in the dispersion direction, tuned to detector defects, better describes the wavelength solution than a single, continuous polynomial \citep{milakovic2020}.
